---
title: "UNIV_BASEBALL_RANKING"
format:
  html:
    page-layout: full
---

```{r setup}
source("common_site.R", local = TRUE)

top_team_count <- min(10, nrow(current_team_table))
top_league_count <- min(10, nrow(current_league_table))

home_games_data <- games_display |>
  transmute(
    event_id,
    date = format(gamedate, "%Y-%m-%d"),
    date_label,
    gametype,
    team1_name,
    team1_url,
    team1_color,
    team1_rate_before,
    score1,
    score2,
    score_label,
    team2_name,
    team2_url,
    team2_color,
    team2_rate_before,
    total_level,
    rating_move_value
  )

home_games_json <- toJSON(home_games_data, dataframe = "rows", auto_unbox = TRUE)
today_value <- format(Sys.Date(), "%Y-%m-%d")
```

::: {.minimal-hero}
<div class="minimal-kicker">LATEST SNAPSHOT</div>
<h1 class="minimal-title">UNIV_BASEBALL_RANKING</h1>
<div class="hero-meta-strip">
  <span>SNAPSHOT `r fmt_date(latest_snapshot_date)`</span>
  <span>LATEST GAME `r fmt_date(latest_game_date)`</span>
  <span>UNIV `r nrow(current_team_table)`</span>
  <span>LEAGUE `r nrow(current_league_table)`</span>
</div>
:::

::: {.anchor-nav}
<a href="#latest-univ-ranking">LATEST UNIV RANKING</a>
<a href="#latest-league-ranking">LATEST LEAGUE RANKING</a>
<a href="#daily-games">DAILY GAMES</a>
:::

## LATEST UNIV RANKING {#latest-univ-ranking}

```{r latest-univ-ranking}
div(
  class = "table-shell",
  build_university_table(
    current_team_table |> slice_head(n = top_team_count),
    page_size = top_team_count,
    show_pagination = FALSE
  )
)
```

<div class="section-actions">
  <a href="explore.html#university-browser" class="directory-link">すべての大学を見る</a>
</div>

## LATEST LEAGUE RANKING {#latest-league-ranking}

```{r latest-league-ranking}
div(
  class = "table-shell",
  build_league_table(
    current_league_table |> slice_head(n = top_league_count),
    page_size = top_league_count,
    show_pagination = FALSE
  )
)
```

<div class="section-actions">
  <a href="explore.html#league-browser" class="directory-link">すべてのリーグを見る</a>
</div>

## DAILY GAMES {#daily-games}

```{r daily-games-controls}
div(
  class = "game-panel",
  div(
    class = "game-panel-head",
    div(
      class = "browser-controls browser-controls-wide",
      div(
        class = "control-block control-block-year",
        tags$label(`for` = "home-games-date", class = "control-label", "DATE"),
        tags$input(
          id = "home-games-date",
          class = "control-input",
          type = "date",
          value = today_value
        )
      ),
      div(
        class = "control-block control-block-year",
        tags$label(`for` = "home-games-sort", class = "control-label", "SORT"),
        tags$select(
          id = "home-games-sort",
          class = "control-input",
          tags$option(value = "LATEST", "LATEST"),
          tags$option(value = "LEVEL", "TOTAL RATE"),
          tags$option(value = "MOVE", "RATE MOVE")
        )
      ),
      div(
        class = "control-block control-block-year",
        tags$label(`for` = "home-games-direction", class = "control-label", "ORDER"),
        tags$select(
          id = "home-games-direction",
          class = "control-input",
          tags$option(value = "DESC", "DESC"),
          tags$option(value = "ASC", "ASC")
        )
      )
    ),
    tags$div(id = "home-games-count", class = "table-count")
  ),
  tags$div(id = "home-games-table")
)
```

```{r daily-games-script}
home_games_script <- paste0(
  "(function(){",
  "const games = ", home_games_json, ";",
  "const input = document.getElementById('home-games-date');",
  "const sortSelect = document.getElementById('home-games-sort');",
  "const directionSelect = document.getElementById('home-games-direction');",
  "const target = document.getElementById('home-games-table');",
  "const count = document.getElementById('home-games-count');",
  "if (!input || !target || !count) { return; }",
  "function esc(v){ return String(v ?? '').replace(/[&<>\\\"']/g, function(ch){ return ({'&':'&amp;','<':'&lt;','>':'&gt;','\\\"':'&quot;',\"'\":'&#39;'})[ch]; }); }",
  "function sortRows(rows){",
  "  const key = sortSelect ? sortSelect.value : 'LATEST';",
  "  const direction = directionSelect && directionSelect.value === 'ASC' ? 1 : -1;",
  "  return rows.slice().sort(function(a, b){",
  "    let diff = 0;",
  "    if (key === 'LEVEL') {",
  "      diff = Number(a.total_level) - Number(b.total_level);",
  "    } else if (key === 'MOVE') {",
  "      diff = Number(a.rating_move_value) - Number(b.rating_move_value);",
  "    } else {",
  "      diff = Number(a.event_id) - Number(b.event_id);",
  "    }",
  "    if (diff === 0) { diff = Number(a.event_id) - Number(b.event_id); }",
  "    return diff * direction;",
  "  });",
  "}",
  "function sortLabel(label, key){",
  "  const active = sortSelect ? sortSelect.value : 'LATEST';",
  "  const dir = directionSelect && directionSelect.value === 'ASC' ? ' ↑' : ' ↓';",
  "  return active === key ? label + dir : label;",
  "}",
  "function render(){",
  "  const value = input.value;",
  "  const filtered = games.filter(function(row){ return row.date === value; });",
  "  const rows = sortRows(filtered);",
  "  count.textContent = rows.length + ' games';",
  "  if (!rows.length) {",
  "    target.innerHTML = '<div class=\"empty-state\">NO GAMES</div>';",
  "    return;",
  "  }",
  "  const html = rows.map(function(row){",
  "    return '<tr>' +",
  "      '<td>' + esc(row.gametype) + '</td>' +",
  "      '<td class=\"matchup-col\"><a href=\"' + esc(row.team1_url) + '\" style=\"color:' + esc(row.team1_color) + '\" class=\"team-link-inline\">' + esc(row.team1_name) + '</a><small> (' + esc(Number(row.team1_rate_before).toFixed(1)) + ')</small><span class=\"score-inline\">' + esc(row.score_label) + '</span><a href=\"' + esc(row.team2_url) + '\" style=\"color:' + esc(row.team2_color) + '\" class=\"team-link-inline\">' + esc(row.team2_name) + '</a><small> (' + esc(Number(row.team2_rate_before).toFixed(1)) + ')</small></td>' +",
  "      '<td>' + esc(Number(row.total_level).toFixed(1)) + '</td>' +",
  "      '<td>' + esc(Number(row.rating_move_value).toFixed(1)) + '</td>' +",
  "    '</tr>';",
  "  }).join('');",
  "  target.innerHTML = '<div class=\"table-shell compact-table-shell\"><table class=\"compact-data-table\"><thead><tr><th>TYPE</th><th>MATCHUP</th><th data-sort-key=\"LEVEL\" style=\"cursor:pointer\">' + esc(sortLabel('TOTAL RATE', 'LEVEL')) + '</th><th data-sort-key=\"MOVE\" style=\"cursor:pointer\">' + esc(sortLabel('RATE MOVE', 'MOVE')) + '</th></tr></thead><tbody>' + html + '</tbody></table></div>';",
  "}",
  "target.addEventListener('click', function(event){",
  "  const header = event.target.closest('th[data-sort-key]');",
  "  if (!header || !sortSelect || !directionSelect) { return; }",
  "  const key = header.getAttribute('data-sort-key');",
  "  if (sortSelect.value === key) {",
  "    directionSelect.value = directionSelect.value === 'ASC' ? 'DESC' : 'ASC';",
  "  } else {",
  "    sortSelect.value = key;",
  "    directionSelect.value = 'DESC';",
  "  }",
  "  render();",
  "});",
  "input.addEventListener('change', render);",
  "if (sortSelect) { sortSelect.addEventListener('change', render); }",
  "if (directionSelect) { directionSelect.addEventListener('change', render); }",
  "render();",
  "})();"
)

tags$script(HTML(home_games_script))
```
