---
title: "UNIV_BASEBALL_RANKING"
format:
  html:
    page-layout: full
---

```{r setup}
source("common_site.R", local = TRUE)

top_team_count <- min(10, nrow(current_team_table))
top_league_count <- min(10, nrow(current_league_table))

home_games_data <- games_display |>
  transmute(
    date = format(gamedate, "%Y-%m-%d"),
    date_label,
    gametype,
    team1_name,
    team1_url,
    team1_color,
    score1,
    score2,
    team2_name,
    team2_url,
    team2_color,
    rating_move_label
  )

home_games_json <- toJSON(home_games_data, dataframe = "rows", auto_unbox = TRUE)
today_value <- format(Sys.Date(), "%Y-%m-%d")
```

::: {.minimal-hero}
<div class="minimal-kicker">LATEST SNAPSHOT</div>
<h1 class="minimal-title">UNIV_BASEBALL_RANKING</h1>
<div class="hero-meta-strip">
  <span>SNAPSHOT `r fmt_date(latest_snapshot_date)`</span>
  <span>LATEST GAME `r fmt_date(latest_game_date)`</span>
  <span>UNIV `r nrow(current_team_table)`</span>
  <span>LEAGUE `r nrow(current_league_table)`</span>
</div>
:::

::: {.anchor-nav}
<a href="#latest-univ-ranking">LATEST UNIV RANKING</a>
<a href="#latest-league-ranking">LATEST LEAGUE RANKING</a>
<a href="#key-games">KEY GAMES</a>
<a href="#daily-games">DAILY GAMES</a>
:::

## LATEST UNIV RANKING {#latest-univ-ranking}

```{r latest-univ-ranking}
div(
  class = "table-shell",
  build_university_table(
    current_team_table |> slice_head(n = top_team_count),
    page_size = top_team_count,
    show_pagination = FALSE
  )
)
```

<div class="section-actions">
  <a href="explore.html#university-browser" class="directory-link">すべての大学を見る</a>
</div>

## LATEST LEAGUE RANKING {#latest-league-ranking}

```{r latest-league-ranking}
div(
  class = "table-shell",
  build_league_table(
    current_league_table |> slice_head(n = top_league_count),
    page_size = top_league_count,
    show_pagination = FALSE
  )
)
```

<div class="section-actions">
  <a href="explore.html#league-browser" class="directory-link">すべてのリーグを見る</a>
</div>

## KEY GAMES {#key-games}

```{r key-games}
div(
  class = "feature-grid",
  build_highlight_card(highest_level_game, "HIGHEST LEVEL GAME"),
  build_highlight_card(largest_movement_game, "BIGGEST RATING MOVE")
)
```

## DAILY GAMES {#daily-games}

```{r daily-games-controls}
div(
  class = "game-panel",
  div(
    class = "game-panel-head",
    tags$label(`for` = "home-games-date", class = "control-label", "DATE"),
    tags$input(
      id = "home-games-date",
      class = "control-input",
      type = "date",
      value = today_value
    ),
    tags$div(id = "home-games-count", class = "table-count")
  ),
  tags$div(id = "home-games-table")
)
```

```{r daily-games-script}
home_games_script <- paste0(
  "(function(){",
  "const games = ", home_games_json, ";",
  "const input = document.getElementById('home-games-date');",
  "const target = document.getElementById('home-games-table');",
  "const count = document.getElementById('home-games-count');",
  "if (!input || !target || !count) { return; }",
  "function esc(v){ return String(v ?? '').replace(/[&<>\\\"']/g, function(ch){ return ({'&':'&amp;','<':'&lt;','>':'&gt;','\\\"':'&quot;',\"'\":'&#39;'})[ch]; }); }",
  "function render(){",
  "  const value = input.value;",
  "  const rows = games.filter(function(row){ return row.date === value; });",
  "  count.textContent = rows.length + ' games';",
  "  if (!rows.length) {",
  "    target.innerHTML = '<div class=\"empty-state\">NO GAMES</div>';",
  "    return;",
  "  }",
  "  const html = rows.map(function(row){",
  "    return '<tr>' +",
  "      '<td>' + esc(row.gametype) + '</td>' +",
  "      '<td class=\"matchup-col\"><a href=\"' + esc(row.team1_url) + '\" style=\"color:' + esc(row.team1_color) + '\" class=\"team-link-inline\">' + esc(row.team1_name) + '</a><span class=\"score-inline\">' + esc(row.score1) + ' - ' + esc(row.score2) + '</span><a href=\"' + esc(row.team2_url) + '\" style=\"color:' + esc(row.team2_color) + '\" class=\"team-link-inline\">' + esc(row.team2_name) + '</a></td>' +",
  "      '<td>' + esc(row.rating_move_label) + '</td>' +",
  "    '</tr>';",
  "  }).join('');",
  "  target.innerHTML = '<div class=\"table-shell compact-table-shell\"><table class=\"compact-data-table\"><thead><tr><th>TYPE</th><th>MATCHUP</th><th>RATING MOVE</th></tr></thead><tbody>' + html + '</tbody></table></div>';",
  "}",
  "input.addEventListener('change', render);",
  "render();",
  "})();"
)

tags$script(HTML(home_games_script))
```
